\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{setspace} % Add this package for line spacing
\setstretch{1.15} % Adjust line spacing as desired
\name{Dylan}{Chen}
\newcommand*{\customcventry}[7][.12em]{
\begin{tabular}{@{}l}
{\bfseries #4} \textbf{#3}\\
{\itshape #2}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5}
\end{tabular}
\ifx&#7&%
\else{\\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}
\begin{document}
\makecvtitle
\vspace*{-16mm}
\vspace{4pt}
\begin{center}
  {\large \textbf{Senior Front-end Developer}}\\[8pt]
  \faMobile\enspace +886 931768323 \hspace{20pt} 
  \faEnvelope\enspace \href{mailto:easycard32145@gmail.com}{easycard32145@gmail.com} \hspace{20pt} 
  \faHome\enspace Taipei City \\[6pt]
  \faLinkedin\enspace \href{https://www.linkedin.com/in/dylan-chen-92366b1b0/}{dylan-chen-92366b1b0} \hspace{20pt} 
  \faGithub\enspace \href{https://github.com/gary880}{github.com/gary880}
\end{center}
\vspace{8pt}
 

\section{ Experience}
\customcventry{08/2024 ‐ present}{\textbf{91APP}}{Senior Front-end Developer,}{Taipei City, Taiwan}{}{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item \textbf{Established AI-assisted code review process}, reducing PR review time by 42\% through survey-validated automation while significantly improving code quality and development efficiency.
\item \textbf{Optimized CMS backend rendering performance}, reducing unnecessary component re-renders and substantially enhancing system performance to support increased user traffic.
\item \textbf{Led standardization of development documentation}, streamlining new employee onboarding from 3 months to 2 months and improving team productivity.
\item \textbf{Spearheaded Q3 core revenue feature delivery}, successfully developed and launched CMS drag-and-drop editor from POC to production, creating new monetization opportunities as a premium paid service.
\item \textbf{Proactively coordinated with Product Owners and QA teams} to synchronize project progress and mitigate deployment risks, ensuring 100\% on-time delivery of Q3 features.
\item \textbf{Established technical knowledge-sharing culture}, initiating and facilitating team book clubs that enhanced cross-team collaboration and accelerated professional development.
\item \textbf{Mentored 2 junior engineers}, providing technical guidance and accelerating their integration into the team within 3 months through structured coaching programs.
\end{itemize}
}

\customcventry{07/2023 ‐ 07/2024}{\textbf{SINBON Electronics}}{Software Engineer,}{New Taipei City, Taiwan}{}{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Integrated front-end testing frameworks (e.g., Jest, React Testing Library) to enforce code quality and reliability.
\item Built an Apple Watch application to seamlessly transmit health data to mobile devices, enhancing real-time monitoring capabilities.
\item Developed a React Native application for Ebike that enabled seamless communication with Ebikes via Bluetooth, allowing for real-time data retrieval.
\item Implemented power management features that resulted in a 40\% decrease in energy consumption when the app was running in the background, significantly improving the user experience.
\item Conducted code reviews for junior developers, ensuring high code quality standards.
\end{itemize}
}

\customcventry{04/2022 ‐ 07/2023}{\textbf{Colerate}}{Front-end Developer,}{Taipei City, Taiwan}{}{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Developed responsive web interfaces for an online quiz system and dashboard using Material UI, enhancing user engagement and experience.
\item Collaborated closely with project managers and designers to translate design concepts into functional, high-quality code.
\item Boosted online visibility through the implementation of highly effective SEO strategies, achieving Lighthouse SEO score increase from 82 to 100.
\end{itemize}
}

\section{Education}

\customcventry{2017-2021}{\color{blue}\href{https://www.ccu.edu.tw/}{National Chung Cheng University}}{Bachelor of Communication Engineering}{Chiayi, Taiwan}{}{}

\section{Skills}

\begin{itemize}[label=\textbullet]
  \item \textbf{Frontend Frameworks \& Libraries:} React (Hooks, Redux, React Router), React Native, Material-UI, Tailwind CSS
  \item \textbf{Programming Languages:} TypeScript, JavaScript, HTML5, CSS3, Swift
  \item \textbf{Testing \& Quality Assurance:} Jest, React Testing Library, Unit Testing
  \item \textbf{Build \& Development Tools:} Git, Docker, Webpack, CI/CD Pipelines
  \item \textbf{Backend Development:} Node.js, Express, RESTful APIs
  \item \textbf{Design \& Prototyping:} Figma, Responsive Web Design
\end{itemize}

\section{Core Competencies}

\begin{itemize}[label=\textbullet]
  \item \textbf{Leadership \& Mentoring:} junior developer coaching, technical knowledge transfer, structured onboarding
  \item \textbf{Cross-functional Collaboration:} Product Owner coordination, QA collaboration, Agile methodologies, risk management
  \item \textbf{Project Management:} Feature delivery optimization, quality assurance processes, roadmap planning
  \item \textbf{Technical Expertise:} Frontend architecture design, performance optimization, scalable component development, code review automation
\end{itemize}
\section{Languages}

\begin{multicols}{2}
  \begin{itemize}[label=\textbullet]
    \item \textbf{Chinese} [Native]
    \item \textbf{English} [Advanced]
  \end{itemize}
\end{multicols}

\end{document}
